Fast Sorting on Modern Computers

### 2005-08-01 docs/tech_report/merge.tex
renamed double_aligned_tiled_mergesort

\sixplot{algorithm_n_0.eps}{algorithm_s_0.eps}{base_mergesort_0.eps}{double_aligned_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{mergesorts}

>>>>

\sixplot{algorithm_n_0.eps}{algorithm_s_0.eps}{base_mergesort_0.eps}{double_aligned_tiled_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_0.eps}{mergesorts}

### 2005-08-01 docs/tech_report/result_list.tex
spell checking. just noticed the word mergsort, so need to fix it
renamed double_aligned_tiled_mergesort

\label{result_list}
\afterpage{
\smallplot{insertsort}{insertion sort}{}{}{}{}{}
\smallplot{selectsort}{selection sort}{}{}{}{}{}
\smallplot{bubblesort}{bubblesort}{}{}{}{}{}
\smallplot{improved_bubblesort}{improved bubblesort}{}{}{}{}{}
\smallplot{shakersort}{shakersort}{}{}{}{}{}
\smallplot{improved_shakersort}{improved shakersort}{}{}{}{}{}
%
\smallplot{base_heapsort}{base heapsort}{}{}{}{}{}
\smallplot{memory_tuned4_heapsort}{memory-tuned heapsort (4-heap)}{}{}{}{}{}
\smallplot{memory_tuned_heapsort}{memory-tuned heapsort (8-heap)}{}{}{}{}{}
%
\smallplot{algorithm_n}{algorithm n}{}{}{}{}{}
\smallplot{algorithm_s}{algorithm s}{}{}{}{}{}
\smallplot{base_mergesort}{base mergesort}{}{}{}{}{}
\smallplot{tiled_mergesort}{tiled mergesort}{}{}{}{}{}
\smallplot{multi_mergesort}{multi-mergesort}{}{}{}{}{}
\smallplot{double_aligned_mergesort}{double-aligned tiled mergesort}{}{}{}{}{}
\smallplot{double_aligned_multi_mergsort}{double-aligned multi-mergesort}{}{}{}{}{}
%
\smallplot{base_quicksort1}{base quicksort (no median)}{}{}{}{}{}
\smallplot{base_quicksort}{base quicksort (median-of-3)}{}{}{}{}{}
\smallplot{base_quicksort5}{base quicksort (pseudo-median-of-5)}{}{}{}{}{}
\smallplot{base_quicksort7}{base quicksort (pseudo-median-of-7)}{}{}{}{}{}
\smallplot{base_quicksort9}{base quicksort (pseudo-median-of-9)}{}{}{}{}{}
\smallplot{memory_tuned_quicksort}{memory-tuned quicksort}{}{}{}{}{}
\smallplot{multi_quicksort}{multi-quicksort (binary search)}{}{}{}{}{}
\smallplot{multi_quicksort_seq}{multi-quicksort (sequential search)}{}{}{}{}{}
%
\smallplot{base_radixsort}{base radixsort}{}{}{}{}{}
\smallplot{memory_tuned_radixsort}{memory-tuned radixsort}{}{}{}{}{}
\smallplot{aligned_memory_tuned_radixsort}{aligned memory-tuned radixsort}{}{}{}{}{}
%
\smallplot{shellsort}{shellsort}{}{}{}{}{}
\smallplot{improved_shellsort}{improved shellsort}{}{}{}{}{}
}

>>>>

\label{result_list}
\afterpage{
\smallplot{insertsort}{insertion sort}{}{}{}{}{}
\smallplot{selectsort}{selection sort}{}{}{}{}{}
\smallplot{bubblesort}{bubblesort}{}{}{}{}{}
\smallplot{improved_bubblesort}{improved bubblesort}{}{}{}{}{}
\smallplot{shakersort}{shakersort}{}{}{}{}{}
\smallplot{improved_shakersort}{improved shakersort}{}{}{}{}{}
%
\smallplot{base_heapsort}{base heapsort}{}{}{}{}{}
\smallplot{memory_tuned4_heapsort}{memory-tuned heapsort (4-heap)}{}{}{}{}{}
\smallplot{memory_tuned_heapsort}{memory-tuned heapsort (8-heap)}{}{}{}{}{}
%
\smallplot{algorithm_n}{algorithm n}{}{}{}{}{}
\smallplot{algorithm_s}{algorithm s}{}{}{}{}{}
\smallplot{base_mergesort}{base mergesort}{}{}{}{}{}
\smallplot{tiled_mergesort}{tiled mergesort}{}{}{}{}{}
\smallplot{multi_mergesort}{multi-mergesort}{}{}{}{}{}
\smallplot{double_aligned_tiled_mergesort}{double-aligned tiled mergesort}{}{}{}{}{}
\smallplot{double_aligned_multi_mergesort}{double-aligned multi-mergesort}{}{}{}{}{}
%
\smallplot{base_quicksort1}{base quicksort (no median)}{}{}{}{}{}
\smallplot{base_quicksort}{base quicksort (median-of-3)}{}{}{}{}{}
\smallplot{base_quicksort5}{base quicksort (pseudo-median-of-5)}{}{}{}{}{}
\smallplot{base_quicksort7}{base quicksort (pseudo-median-of-7)}{}{}{}{}{}
\smallplot{base_quicksort9}{base quicksort (pseudo-median-of-9)}{}{}{}{}{}
\smallplot{memory_tuned_quicksort}{memory-tuned quicksort}{}{}{}{}{}
\smallplot{multi_quicksort}{multi-quicksort (binary search)}{}{}{}{}{}
\smallplot{multi_quicksort_seq}{multi-quicksort (sequential search)}{}{}{}{}{}
%
\smallplot{base_radixsort}{base radixsort}{}{}{}{}{}
\smallplot{memory_tuned_radixsort}{memory-tuned radixsort}{}{}{}{}{}
\smallplot{aligned_memory_tuned_radixsort}{aligned memory-tuned radixsort}{}{}{}{}{}
%
\smallplot{shellsort}{shellsort}{}{}{}{}{}
\smallplot{improved_shellsort}{improved shellsort}{}{}{}{}{}
}

### 2005-08-01 docs/tech_report/software_predictor.tex
renamed double_aligned_tiled_mergesort

\sixplot{base_quicksort_0.eps}{base_quicksort9_0.eps}{memory_tuned_quicksort_0.eps}{multi_quicksort_0.eps}{sequential_multi_quicksort_0.eps}{}{base, memory-tuned and multi quicksorts and base quicksort (pseudo-median-of-9)}
\sixplot{base_quicksort1_0.eps}{base_quicksort_0.eps}{base_quicksort5_0.eps}{base_quicksort7_0.eps}{base_quicksort9_0.eps}{}{base quicksort without a median, with median of 3, and with pseudo-medians of 5, 7 and 9}
\sixplot{algorithm_n_0.eps}{algorithm_n_1.eps}{algorithm_s_0.eps}{algorithm_s_1.eps}{}{}{Knuth's mergesorts}
\sixplot{base_mergesort_0.eps}{base_mergesort_1.eps}{base_mergesort_2.eps}{base_mergesort_3.eps}{base_mergesort_4.eps}{base_mergesort_5.eps}{base mergesort}
\sixplot{double_aligned_mergesort_0.eps}{double_aligned_mergesort_1.eps}{double_aligned_mergesort_2.eps}{double_aligned_mergesort_3.eps}{double_aligned_mergesort_4.eps}{double_aligned_mergesort_5.eps}{double-aligned tiled mergesort - part 1}
\sixplot{double_aligned_mergesort_6.eps}{double_aligned_mergesort_7.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_1.eps}{double_aligned_multi_mergesort_2.eps}{double_aligned_multi_mergesort_3.eps}{double-aligned tiled mergesort - part 2, and double multi mergesort - part 1}
\sixplot{double_aligned_multi_mergesort_4.eps}{double_aligned_multi_mergesort_5.eps}{double_aligned_multi_mergesort_6.eps}{double_aligned_multi_mergesort_7.eps}{double_aligned_multi_mergesort_8.eps}{double_aligned_multi_mergesort_9.eps}{double-aligned multi-mergesort - part 2}

>>>>

\sixplot{base_quicksort_0.eps}{base_quicksort9_0.eps}{memory_tuned_quicksort_0.eps}{multi_quicksort_0.eps}{sequential_multi_quicksort_0.eps}{}{base, memory-tuned and multi quicksorts and base quicksort (pseudo-median-of-9)}
\sixplot{base_quicksort1_0.eps}{base_quicksort_0.eps}{base_quicksort5_0.eps}{base_quicksort7_0.eps}{base_quicksort9_0.eps}{}{base quicksort without a median, with median of 3, and with pseudo-medians of 5, 7 and 9}
\sixplot{algorithm_n_0.eps}{algorithm_n_1.eps}{algorithm_s_0.eps}{algorithm_s_1.eps}{}{}{Knuth's mergesorts}
\sixplot{base_mergesort_0.eps}{base_mergesort_1.eps}{base_mergesort_2.eps}{base_mergesort_3.eps}{base_mergesort_4.eps}{base_mergesort_5.eps}{base mergesort}
\sixplot{double_aligned_tiled_mergesort_0.eps}{double_aligned_tiled_mergesort_1.eps}{double_aligned_tiled_mergesort_2.eps}{double_aligned_tiled_mergesort_3.eps}{double_aligned_tiled_mergesort_4.eps}{double_aligned_tiled_mergesort_5.eps}{double-aligned tiled mergesort - part 1}
\sixplot{double_aligned_tiled_mergesort_6.eps}{double_aligned_tiled_mergesort_7.eps}{double_aligned_multi_mergesort_0.eps}{double_aligned_multi_mergesort_1.eps}{double_aligned_multi_mergesort_2.eps}{double_aligned_multi_mergesort_3.eps}{double-aligned tiled mergesort - part 2, and double multi mergesort - part 1}
\sixplot{double_aligned_multi_mergesort_4.eps}{double_aligned_multi_mergesort_5.eps}{double_aligned_multi_mergesort_6.eps}{double_aligned_multi_mergesort_7.eps}{double_aligned_multi_mergesort_8.eps}{double_aligned_multi_mergesort_9.eps}{double-aligned multi-mergesort - part 2}
